\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-10 paper.tex
autoencoder neural network

\begin{figure}
  \includegraphics[width=\linewidth]{nnlm.png}
  \caption{Figure 4: Neural Network Based Mapping}
  \label{fig:nnlm}
\end{figure}
\subsubsection{Autoencoder (GAN)}
An autoencoder is a type of neural network that learns to label dimensions in an unsupervised manner. Figure 5 shows that an autoencoder is composed of two parts: the input side, marked as $X$, and the reconstruction (output) side, marked as $X'$. The $X$ tries to learn a distributed representation of the original data that aims to reduce the dimensions, and the $X'$ side is where the autoencoder tries to generate from the reduced representation as close as possible to its original input, hence its name, reconstruction. 
\paragraph{Basic Architecture of Autoencoder}
\begin{figure}
  \includegraphics[width=\linewidth]{Autoencoder_structure.png}
  \caption{Figure 5: Schematic structure of an autoencoder with 3 fully connected hidden layers. The code (z, or h for reference in the text) is the most internal layer.}
  \label{fig:autoencoder}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{nnlm.png}
  \caption{Figure 4: Neural Network Based Mapping}
  \label{fig:nnlm}
\end{figure}
\subsubsection{Autoencoder (GAN)}
An autoencoder is a type of neural network that learns to label dimensions in an unsupervised manner. Figure 5 shows that an autoencoder is composed of two parts: the input side, marked as $X$, and the reconstruction (output) side, marked as $X'$. The $X$ tries to learn a distributed representation of the original data that aims to reduce the dimensions, and the $X'$ side is where the autoencoder tries to generate from the reduced representation as close as possible to its original input, hence its name, reconstruction. 
\begin{figure}
  \includegraphics[width=\linewidth]{Autoencoder_structure.png}
  \caption{Figure 5: Schematic structure of an autoencoder with 3 fully connected hidden layers. The code (z, or h for reference in the text) is the most internal layer.}
  \label{fig:autoencoder}
\end{figure}
\paragraph{Basic Architecture of Autoencoder}
An autoencoder consists of two parts, the encoder and the decoder, which can be defined as transitions $\psi$ and $\phi$, such that:
\begin{align*}
& \psi : \chi \mapsto \mathfrak{F} \\
& \phi : \mathfrak{F} \mapsto \chi \\
& \psi, \phi = arg_{\psi, \phi} min \lvert \chi - (\psi * \phi) \chi \rvert
\end{align*}
In the simplest form, we assume there is only one hidden layer. The encoder stage of the autoencoder takes input $x \in \mathbb{R}^{d} = \chi$ and maps it to $\mathbf{h} \in \mathbb{R}^{p} = \mathfrak{F}$. \\
\begin{align*}
\mathbf{h} = \delta (\mathbf{W}x + \mathbf{b})
\end{align*}
This image $\mathbf{h}$ is the code section shown in Figure 5. $\delta$ is normally a sigmoid function defined as following: \\
\begin{align*}
S(x) = \frac{1}{1 + e^{-x}} = \frac{e^x}{e^x + 1}
\end{align*}
$\mathbf{W}$ is a weight matrix and $\mathbf{b}$ is a bias vector. The initializations of these two variables are random. They will be learnt iteratively through \textbf{backpropagation}. \\
